\documentclass[10pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\title{Review Note Page}
\author{}
\date{December 2021}

\begin{document}
\scriptsize
$\textbf{N} = \{ 0, 1, 2, 3, ...\}$,
$\textbf{Z} = \{0, 1, -1, 2, -2, ...\}$,
$\textbf{Q} = \{\left(\frac{a}{b}\right): (a, b) \in \textbf{Z}\}$ \\\\
Implies: \hspace{4cm} Biconditional:\\
\begin{tabular}{c|c|c}
    A & B & $A \rightarrow B$ \\
    \hline
    0 & 0 & 1 \\
    0 & 1 & 1 \\
    1 & 0 & 0 \\
    1 & 1 & 1 \\
\end{tabular} \hspace{2cm}
\begin{tabular}{c|c|c}
    A & B & A iff B \\
    \hline
    0 & 0 & 1 \\
    0 & 1 & 0 \\
    1 & 0 & 0 \\
    1 & 1 & 1 \\
\end{tabular} \\

A \textbf{well formed formula} of the set of vars $\mathcal{P}$: \\
- 1 or 0 (true or false) \\
- A variable from $\mathcal{P}$. \\
- A conjunction of two formulas using a logically complete set of ops (e.g. $\{\wedge, \neg\}$)

A \textbf{truth assignment} is a map of a set $\mathcal{P}$ to $\mathbf{B}$ (bools). \\
\[t(A \wedge B) = t(A) \wedge t(B), t(\neg{A}) = \neg{t(A)}\]
The pointy gate is OR. The triangular gate is NOT. \\
$\neg{\forall A} = \exists A, \neg{\exists A} = \forall A$,
$|\mathcal{P}(x)| = 2^{|x|}$

A group is must have these three properties: \\
- Associative - $(A \cdot B) \cdot C = A \cdot (B \cdot C)$ \\
- There exists an identity - $X \cdot i = i \cdot X = X$ \\
- There exists an inverse to create the identity - $X \cdot Y = i$ \\

Number Theory is simple: \\
- 0 as a constant \\
- The comparision operator < \\
- Functions: successor, addition, multiplication, exponentiation, equality. \\

Relation (R): \\
- Reflexive: a is related to itself ($a R a$) \\
- Symmetric: goes both ways ($a R b \rightarrow b R a$) \\
- Transitive: if $a R b$ and $b R c, a R c$ \\

A regular language: \\
- Kleene star - permutations of a string / alphabet \\
- Concatenations of strings \\
- Singletons derivated from the base alphabet \\
- Other regular langs \\

Big O: $(\exists c)(\exists N)(\forall n \geq N)(f(n) \leq cn)$ \\

Graph: an ordered pair (V, E) where V is a finite, nonempty set of identifiers, and E is a set of two-element subsets of V (the edges) \\
Two graphs G and G' are isomorphic if there is a func $\pi(x)$ that maps a point \{v, w\} from G to $\{\pi(v), \pi(w)\}$ from G'. \\
Hamiltonian: cross all points once. Eulerian: cross all edges once. The sum of the degrees of all points in a graph must be 2 times the edges (always an even number) \\
log(n!) is about nlogn. \\
A clique is a graph with very possible point connected to each other. The number of edges in a clique of $n$ points is $_nC_2$.

\end{document}
